|

### 2022-07-07 paper/paper.Rmd

```{r penguins-scatmat, out.width="100%", width=10, height=10, fig.cap="Scatterplot matrix of the (standardised) penguins data."}
library(tidyverse)
library(palmerpenguins)
library(GGally)
penguins_data <- penguins[, c(1,3, 4, 5, 6)] %>%
  drop_na() %>%
  mutate(across(where(is.numeric), function(x) (x-mean(x))/sd(x)))
ggscatmat(penguins_data, columns = 2:5, col="species") +
  scale_colour_manual("", values=c("Adelie" = "#5E82B6", "Chinstrap" = "#E19C24", "Gentoo" = "#8FB132")) +
  theme(legend.position = "bottom")
```

>>>>

```{r penguins-scatmat, out.width="100%", width=10, height=10, fig.cap="Scatterplot matrix of the (standardised) penguins data."}
library(tidyverse)
library(palmerpenguins)
library(GGally)
penguins_data <- penguins[, c(1,3, 4, 5, 6)] %>%
  drop_na() %>%
  mutate(across(where(is.numeric), function(x) (x-mean(x))/sd(x))) %>%
  rename("bl"="bill_length_mm",
         "bd"="bill_depth_mm",
         "fl"="flipper_length_mm",
         "bm"="body_mass_g")
ggscatmat(penguins_data, columns = 2:5, col="species") +
  scale_colour_manual("", values=c("Adelie" = "#5E82B6", "Chinstrap" = "#E19C24", "Gentoo" = "#8FB132")) +
  theme(legend.position = "bottom")
```
